Choosing ordinal effect measures for clinical trials

### 2025-06-25 choosing_ordinal_effect_measures.tex
Add Kalbfleisch et al reference

>>>>

Another set of critiques are in
\citet{hartmanPitfallsConcordanceIndex2023}. I haven't understood
these yet but the main concern seems to be that more comparable cases
(in terms of baseline risk) are more likely to have ties. So there's
a tradeoff between relevance of the comparisons (conditioning on
similar baseline risk) and informativeness of the comparisons
(avoiding ties/getting clear "wins").
